Lasso_RCI_Response

### 2024-06-30 Lasso_RCI_Response.Rmd
Fixing Anx LASSO

#wald
   library(aod)
   anx_wald  <- wald.test(b = coef(glm_min_anx),Sigma = vcov(glm_min_anx),Terms= 2:10)
  wald <- wald.test(b = coef(glm_min_anx),Sigma = vcov(glm_min_anx),Terms=2)$result$chi2[1]
  for(i in 3:11){
      wald <- append(wald, wald.test(b = coef(glm_min_anx),Sigma = vcov(glm_min_anx),Terms=i)$result$chi2[1])
  }
  wald
```

@@

#assign variable names
anx_df$Variable <- c(
    paste0("X^2 = ", round(anx_wald$result$chi2[1],2),", p<0.001"),
    paste0("Model R^2 = ", round((R2.min.anx[[1]]*100),3),"%"),
    "Co-occuring BPD", "Days Not Attended", "Age", "Post Functioning", 
    "Post Sense of Wellbeing", "Post PMH", "Post Coping", "Some College",
    "Co-occuring SUD", "Anxiety Disorder",
    "Variable"
    )

>>>>

#wald
   library(aod)
   anx_wald  <- wald.test(b = coef(glm_min_anx),Sigma = vcov(glm_min_anx),Terms= 2:11)
  wald <- wald.test(b = coef(glm_min_anx),Sigma = vcov(glm_min_anx),Terms=2)$result$chi2[1]
  for(i in 3:11){
      wald <- append(wald, wald.test(b = coef(glm_min_anx),Sigma = vcov(glm_min_anx),Terms=i)$result$chi2[1])
  }
  wald
```

@@

#assign variable names
anx_df$Variable <- c(
    paste0("X^2 = ", round(anx_wald$result$chi2[1],2),", p<0.001"),
    paste0("Model R^2 = ", round((R2.min.anx[[1]]*100),3),"%"),
    "Co-occuring BPD",
    "Days Not Attended", 
    "Age", 
    "Post Functioning", 
    "Post Sense of Wellbeing", 
    "Post Positive Mental Health", 
    "Post Coping Ability", 
    "Some College",  
    "Anxiety Disorder", 
    "Co-occuring SUD", 
    "Variable"
    )
